Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-20 VMCAI-revised-version/final.tex
Rearranged a bit the t-liveness section, déjà on commence par parler de la t-liveness et on fait moins de back and forth entre zero-reachability et la t-liveness, comme ça quand on parle de la zero reachability c'est déjà davantage évident pq la t-liveness c'est très proche de la resilience. et aussi du coup quand j'introduit la zero-reachability j'ai rajouté une phrase pour parler du fait que c'est pas le même type de quantificateur ce qui rends la réduction nontriviale

We now recall the
 undecidable \cite{araki1976PN} decision problem of {\em zero-reachability} in reset-VASS of dimension $d$, which consists in, given a
reset-VASS $V=(Q,T)$, and $p(\textbf{u}) \in Q \times \N^d$,
deciding whether $\exists q \in Q ~ p(\textbf{u}) \to^* q(\textbf{0})$.
%
We reduce the zero-reachability problem to the problem of deciding whether a control-transition is live,
which we then reduce to {\sc State-resilience}.
A control-transition $t$ of a reset-VASS is {\em live} in a state $r(\textbf{w})$ if for each $q(\textbf{v}) \in \post^*(r(\textbf{w}))$ there exists two states
 $p(\textbf{u}),p'(\textbf{u'})$ such that $q(\textbf{v}) \to^* p(\textbf{u}) \xrightarrow{t} p'(\textbf{u'}) $. 
%		($t$ is enabled in $p(\textbf{u})$). 
We say that the whole reset-VASS is live if all its control-transitions are
live. This leads to the following problem.

@@

The following Proposition is a variation  to reset-VASS of Theorem~5.5 in \cite{peterson1981petri} originally stated for Petri nets, whose proof can be seen in Appendix~\ref{appendix}%
.
\begin{proposition}\label{liveness reset}
The  zero reachability problem can be reduced to {\sc $t$-liveness}.
\end{proposition}

>>>>

A control-transition $t$ of a reset-VASS is {\em live} in a state $r(\textbf{w})$ if for each $q(\textbf{v}) \in \post^*(r(\textbf{w}))$ there exists two states
 $p(\textbf{u}),p'(\textbf{u'})$ such that $q(\textbf{v}) \to^* p(\textbf{u}) \xrightarrow{t} p'(\textbf{u'}) $. 
%		($t$ is enabled in $p(\textbf{u})$). 
We say that the whole reset-VASS is live if all its control-transitions are
live. This leads to the following problem.

@@

It now remains to argue why {\sc $t$-liveness} is undecidable.
We  recall the
 undecidable \cite{araki1976PN} decision problem of {\em zero-reachability} in reset-VASS of dimension $d$, which consists in, given a
reset-VASS $V=(Q,T)$, and $p(\textbf{u}) \in Q \times \N^d$,
deciding whether $\exists q \in Q ~ p(\textbf{u}) \to^* q(\textbf{0})$.
%
Remark that the quantification over the path is existential rather than universal i.e. 
{\em zero-reachability}
does not asks that zero remains reachable from an initial state $s_0$ at all times but rather, that there exists at least one way to reach it.
Despite this it is possible to reduce 
the {\em zero-reachability problem} 
to
{\sc $t$-liveness}.
The following Proposition is a variation  to reset-VASS of Theorem~5.5 in \cite{peterson1981petri} originally stated for Petri nets, whose proof can be seen in Appendix~\ref{appendix}%
.
\begin{proposition}\label{liveness reset}
The  zero reachability problem can be reduced to {\sc $t$-liveness}.
\end{proposition}
